New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification

### 2025-06-20 paper.tex
Grant number

\acks{All acknowledgements go at the end of the paper before appendices and references.
Moreover, you are required to declare funding (financial activities supporting the
submitted work) and competing interests (related financial activities outside the submitted work).
More information about this disclosure can be found on the JMLR website.}

>>>>

\acks{Research on this paper was partially supported by grant VEGA 2/0172/22 Classification using ensembles of neural networks.  }
